---
title: "final_figures_veg"
output: html_document
---


```{r}
library(lme4)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(car)
library(emmeans)
library(lubridate)
library(lavaan)
library(lavaan.survey)
library(lme4)
library(nlme)
library(lmerTest)
library(piecewiseSEM)
library(MuMIn)
library(car)
library(vegan)
library(lattice)
#library(scales)
library(gganimate)
library(gifski)
library(bayestestR)
library(patchwork)
```




```{r}
rm(list=ls())
```

```{r}
stdError <- function(x) {
  sd(x) / sqrt(length(x))
}
```

```{r}
source("/Users/joshuagilman/Documents/code/thesis/stats/thesis_chapter_1/R_files/constants_new.R")
```


# functions
```{r}
facet_panel_labels_rodent <- list('rodent_control' = "Rodent-access", 'rodent_exclusion' = "Rodent-exclusion")

plot_labeller <- function(variable, value) {
  return(facet_panel_labels_rodent[value])
}
```

# data
```{r}
canopy_cover_step_1 <- model_veg %>%
  select(shelter, year, BRTE_canopy_cover, CETE_canopy_cover, ELEL_canopy_cover, annual_mustard_canopy_cover) 

canopy_cover_shannon_diversity <- diversity(canopy_cover_step_1[3:6], index = "shannon", MARGIN = 1, base = exp(1))

canopy_cover_step_1[["shannon_diversity_canopy_cover"]] <- canopy_cover_shannon_diversity 

canopy_cover_step_2 <- canopy_cover_step_1 %>%
  select(shelter, year, shannon_diversity_canopy_cover)

shannon_diversity_canopy_cover_df <- model_veg %>%
  inner_join(., canopy_cover_step_2, by = c("shelter", "year") )
```



# @BRTE_density 3-way
```{r}
BRTE_density_fig <- shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(BRTE_density), standard_error = stdError(BRTE_density)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Cheatgrass density") ~ "(m" ^ "-2" ~ ")")) + theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_blank(), # cannot figure out how to manually place the facet_strip.
    #axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(0.15, 0.8),
    legend.title = element_blank()
    ) 

# ggsave(path = tc1_figure_bw_photo_path, "BRTE_density_3_way.png", width = 6, height = 3.5)

BRTE_density_fig
```
# @BRTE_cover 3-way
```{r}
# # BRTE_cover with facet strip on the bottom
# BRTE_cover_fig <- shelter_cover_density_new_joined %>%
#   filter(block != 1 & block != 4) %>% 
#   filter(precip_treatment != "control") %>% 
#   dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
#   dplyr::summarise(mean = mean(BRTE_canopy_cover), standard_error = stdError(BRTE_canopy_cover)) %>% 
#   ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Cheatgrass") ~ "(% cover)")) + theme(
#     axis.title.x = element_blank(),
#     axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
#     #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
#     axis.text.x = element_text(vjust = -0.1, size = 12), # cannot figure out how to manually place the facet_strip.
#     axis.text = element_text(size = 10),
#     strip.placement = "outside",
#     #axis.ticks = element_blank(),
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.background = element_blank(),
#     panel.border = element_blank(),
#     axis.line = element_line(colour = "black"),
#     legend.title = element_blank(),
#     legend.position = "none") 

# BRTE_cover_fig without facet strip on the bottom.
BRTE_cover_fig <- shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(BRTE_canopy_cover), standard_error = stdError(BRTE_canopy_cover)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Cheatgrass cover") ~ "(%)")) + theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_text(vjust = -0.1, size = 12), # cannot figure out how to manually place the facet_strip.
    axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 10),
    legend.position = "none",
    legend.title = element_blank()
    ) 

# ggsave(path = tc1_figure_bw_photo_path, "BRTE_cover_3_way.png", width = 6, height = 3.5)

BRTE_cover_fig

```

axis.title.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_text(vjust = -0.1, size = 12), # cannot figure out how to manually place the facet_strip.
    axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.title = element_blank(),
    legend.position = "none")     
    
    

# @CETE_density 3-way
```{r}
CETE_density_fig <- shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(CETE_density), standard_error = stdError(CETE_density)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste(italic("C. testiculata") ~ "(m" ^ "-2" ~ ")"))) + scale_y_continuous(limits = c(0,800)) + theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_blank(), # cannot figure out how to manually place the facet_strip.
    #axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(0.15, 0.99),
    legend.title = element_blank()
    ) 

# ggsave(path = tc1_photo_path, "CETE_density_3_way.png", width = 6, height = 3.5)

CETE_density_fig
```

# @ELEL_density 3-way
```{r}
ELEL_density_fig <- shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(ELEL_density), standard_error = stdError(ELEL_density)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste(italic("E. elymoides") ~ "(m" ^ "-2" ~ ")"))) + theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_blank(), # cannot figure out how to manually place the facet_strip.
    #axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = "none",
    legend.title = element_blank()
    ) 

# ggsave(path = tc1_photo_path, "ELEL_density_3_way.png", width = 6, height = 3.5)

ELEL_density_fig
```
# @Community Density
```{r}
community_density_fig <- model_veg %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(total_density), standard_error = stdError(total_density)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.90, position = position_dodge(width = 0.90)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.90), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Total plant density") ~ "(m" ^ "-2" ~ ")")) + scale_y_continuous(limits = c(0,3000)) + theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_blank(), # cannot figure out how to manually place the facet_strip.
    #axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(0.15, 0.8),
    legend.title = element_blank()
    ) 

community_density_fig
```


# @Community Cover
```{r}
community_cover_fig <- model_veg %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(total_canopy_cover), standard_error = stdError(total_canopy_cover)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.90, position = position_dodge(width = 0.90)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.90), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Total plant cover (%)"))) + scale_y_continuous(limits = c(0,1)) + theme(
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_blank(), # cannot figure out how to manually place the facet_strip.
    #axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = "none",
    legend.title = element_blank()
    ) 

community_cover_fig
```



# @Shannon D. 3-way
```{r}
SD_density_fig <- shannon_diversity_canopy_cover_df %>%
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(shannon_diversity_canopy_cover), standard_error = stdError(shannon_diversity_canopy_cover)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.80, position = position_dodge(width = 0.80)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.80), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + facet_wrap(. ~ rodent_treatment, labeller = plot_labeller, strip.position = "bottom") + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste("Shannon diversity"))) + theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_text(vjust = -0.1, size = 12), # cannot figure out how to manually place the facet_strip.
    axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 10),
    legend.position = "none",
    legend.title = element_blank()
    ) 

# ggsave(path = tc1_figure_bw_photo_path, "STORY_shannon_rodent_burn_year.png", width = 6, height = 3.5)

SD_density_fig

```



# @other
```{r}
shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(BRTE_density), standard_error = stdError(BRTE_density)) %>% 
  ungroup() %>%
  slice(1 ,4, 5, 6, 7, 8) %>%
  mutate(new_column = row_number()) %>%
  ggplot(aes(x = new_column, y = mean)) + geom_bar(stat = "identity", fill = "white", color = "black") + ylab(expression(paste(italic("Bromus tectorum") ~ "(m" ^ "-2" ~ ")"))) + theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.y = element_blank(),
    # axis.line.y = element_blank(),
    # axis.ticks.y = element_blank(),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text = element_text(size = 10),
    #strip.placement = "outside",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(0.25, 0.8),
    legend.title = element_blank()
    ) #+ ggsave(path = tc1_photo_path, "BRTE_dens_alt.png", width = 5, height = 2.2)
```
axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()

```{r}


shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, burn_treatment) %>%
  dplyr::summarise(mean = mean(BRTE_density), standard_error = stdError(BRTE_density)) %>% 
  ggplot(aes(x = burn_treatment, y = mean, fill = rodent_treatment)) + geom_bar(stat = "identity", width = 0.90, position = position_dodge(width = 0.90)) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(width = 0.90), stat = "identity") + scale_x_discrete(labels = c("burn" = "Burn", "re_burn" = "Reburn")) + ylab(expression(paste(italic("Bromus tectorum") ~ "(m" ^ "-2" ~ ")"))) + theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_text(vjust = -0.1, size = 12), # cannot figure out how to manually place the facet_strip.
    axis.text = element_text(size = 10),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.title = element_blank(),
    legend.position = c(0.18, 0.80)) #+ ggsave(path = tc1_photo_path, "BRTE_density_rodent_burn_2018.png", width = 6, height = 3.5)



```




```{r}
shelter_cover_density_new_joined %>%
  filter(block != 1 & block != 4) %>% 
  filter(precip_treatment != "control") %>% 
  dplyr::group_by(rodent_treatment, precip_treatment) %>%
  dplyr::summarise(mean = mean(ELEL_density), standard_error = stdError(ELEL_density)) %>% 
  ggplot(aes(x = rodent_treatment, y = mean, fill = precip_treatment)) + geom_bar(stat = "identity", width = 0.70, position = position_dodge()) + geom_errorbar(aes(ymin = mean - standard_error, ymax = mean + standard_error, width = 0.1), position = position_dodge(0.70), stat = "identity") + scale_x_discrete(labels = c("rodent_control" = "Rodent-access", "rodent_exclusion" = "Rodent-exclusion")) + scale_fill_manual(labels = c("Drought", "Drought-pulse"), values = c("grey80", "grey20")) + ylab(expression(paste(italic("Elymus elymoides") ~ "(m" ^ "-2" ~ ")"))) + theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 8),
    #axis.text.x = element_text(margin = margin(t = 0, r = 10, b = 0, l = 20), size = 12),
    axis.text.x = element_text(vjust = -0.1, size = 8), # cannot figure out how to manually place the facet_strip.
    axis.text = element_text(size = 8),
    strip.placement = "outside",
    #axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.title = element_blank(),
    legend.position = c(0.28, 0.80)) #+ ggsave(path = tc1_photo_path, "ELEL_density_2_way.png", width = 4, height = 3)
```

#.
# Fig. BRTE
```{r}
BRTE_density_fig
BRTE_cover_fig
```

```{r}
(BRTE_density_fig) / (BRTE_cover_fig) + plot_layout(ncol = 1, nrow = 2, heights = c(1,1)) & plot_annotation(tag_levels = 'A', title = "Figure 2") & theme(
   plot.title = element_text(size = 24),
   plot.tag = element_text(size = 16),
   plot.subtitle = element_text(size = 10))
ggsave(path = tc1_figure_bw_photo_path, "BRTE_figure.png", height = 6, width = 5, scale = 1.3)
```






#.
# Fig. Community
```{r}
community_density_fig
community_cover_fig
SD_density_fig
```

```{r}
(community_density_fig) / (community_cover_fig) + (SD_density_fig) + plot_layout(ncol = 1, nrow = 3, heights = c(1,1,1)) & plot_annotation(tag_levels = 'A', title = "Figure 3") & theme(
   plot.title = element_text(size = 24),
   plot.tag = element_text(size = 16),
   plot.subtitle = element_text(size = 10))
ggsave(path = tc1_figure_bw_photo_path, "community_figure.png", height = 6, width = 4.5, scale = 1.5)
```

