---
title: "SEM_analysis"
output: html_document
---

# library
```{r}
library(ggplot2)
library(tidyverse)
library(vegan)
# library(lavaan)
# library(lavaan.survey)
library(lme4)
library(piecewiseSEM) # this is the developmental version of the package.
library(devtools)
```
get rid of a package that has been installed:


# notes
how to install the developmental version:
https://github.com/jslefche/piecewiseSEM

error with the updated version:
https://stackoverflow.com/questions/43350715/extracting-path-coefficients-of-piecewise-sem-structural-equation-model

lefcheck issues:
https://www.giters.com/jslefche/piecewiseSEM/issues


The newest version of the package (2.1.2) changed a whole bunch of things (see github.com/sflefche/piecewiseSEM). That made it so the lmer code would not work. 


```{r}
rm(list=ls())
```


# source
```{r}
source("/Users/joshuagilman/Documents/code/thesis/stats/thesis_chapter_1/R_files/constants_new.R")
```



# functions
```{r}
# model visualization
model_visualization <- function(model) {
  hist(residuals(model))
  plot(model)
}

# normality visualizations
normality_visualization <- function(model) {
  hist(resid(model)) #residuals all look OK
  plot(model,3) 
  plot(model,1)
  plot(model,2)
  plot(model,4)
}

# heterogenerity of variance visualizations
boxplot_visualization <- function(dataframe, x_var, y_var) {
  x_var <- enquo(x_var)
  y_var <- enquo(y_var)
  
  dataframe %>%
    ggplot(aes(x = !! x_var, y = !! y_var)) + geom_boxplot()
}

# num zeros in data
num_zeros_in_data <- function(dataframe, response_variable) {
  num_zeros = 0
  for (row in 1:nrow(dataframe)) {
  if (dataframe[row, response_variable] == 0) {
    num_zeros = 1 + num_zeros
    }
  }
  return(num_zeros)
}

```



# filter data
```{r}
# WITHOUT WP DATA
SEM_df <- shelter_cover_density_new_joined %>% 
  filter(block != 1 & block != 4 & precip_treatment != "control" & precip_treatment != "post_control") %>% 
  mutate(rodent_bin = ifelse(rodent_treatment == "rodent_control", 0, 1), precip_bin = ifelse(precip_treatment == "drought", 0,1), year_bin = ifelse(year == 2018, 0,1), burn_bin = ifelse(burn_treatment == "burn", 0,1), propagule_bin = ifelse(propagule_pressure == "no", 0,1)) %>%
  mutate(BRTE_density_sqrt = sqrt(BRTE_density)) %>%
  mutate(BRTE_density_sqrt_sqrt = sqrt(BRTE_density_sqrt)) %>%
  mutate(ELEL_density_sqrt = sqrt(ELEL_density)) %>%
  mutate(ELEL_density_sqrt_sqrt = sqrt(ELEL_density_sqrt)) %>%
  mutate(CETE_density_sqrt = sqrt(CETE_density)) %>%
  mutate(CETE_density_sqrt_sqrt = sqrt(CETE_density_sqrt)) %>%
  mutate(BRTE_canopy_cover_sqrt = sqrt(BRTE_canopy_cover)) %>%
  mutate(BRTE_canopy_cover_sqrt_sqrt = sqrt(BRTE_canopy_cover_sqrt)) %>%
  mutate(ELEL_canopy_cover_sqrt = sqrt(ELEL_canopy_cover)) %>%
  mutate(ELEL_canopy_cover_sqrt_sqrt = sqrt(ELEL_canopy_cover_sqrt)) %>%
  mutate(CETE_canopy_cover_sqrt = sqrt(CETE_canopy_cover)) %>%
  mutate(CETE_canopy_cover_sqrt_sqrt = sqrt(CETE_canopy_cover_sqrt)) %>%
  filter(precip_treatment != "control" & precip_treatment != "post_control") 


SEM_df_2018 <- SEM_df %>%
  filter(year == 2018)

SEM_df_2019 <- SEM_df %>%
  filter(year == 2019)

SEM_df_2020 <- SEM_df %>%
  filter(year == 2020)

```



```{r}
# Join BRTE_density_2018 (from SEM_df_2018) with SEM_df_2019
# we need this as a predictor in the model.
SEM_df_2019_2018_BRTE_predictor <- SEM_df_2018 %>%
  select(BRTE_density, shelter) %>%
  rename(BRTE_density_2018 = BRTE_density) %>%
  inner_join(.,SEM_df_2019, by = "shelter" )

SEM_df_2020_2019_BRTE_predictor <- SEM_df_2019 %>%
  select(BRTE_density, shelter) %>%
  rename(BRTE_density_2019 = BRTE_density) %>%
  inner_join(.,SEM_df_2020, by = "shelter" )

```


#.
# DIVERSITY SEMS

# @data
```{r}
canopy_cover_step_1 <- model_veg %>%
  select(shelter, year, BRTE_canopy_cover, CETE_canopy_cover, ELEL_canopy_cover, annual_mustard_canopy_cover) 

canopy_cover_shannon_diversity <- diversity(canopy_cover_step_1[3:6], index = "shannon", MARGIN = 1, base = exp(1))

canopy_cover_step_1[["shannon_diversity_canopy_cover"]] <- canopy_cover_shannon_diversity 

canopy_cover_step_2 <- canopy_cover_step_1 %>%
  select(shelter, year, shannon_diversity_canopy_cover)

shannon_diversity_canopy_cover_df_SEM <- model_veg %>%
  inner_join(., canopy_cover_step_2, by = c("shelter", "year")) %>% 
  filter(block != 1 & block != 4 & precip_treatment != "control" & precip_treatment != "post_control") %>% 
  mutate(rodent_bin = ifelse(rodent_treatment == "rodent_control", 0, 1), precip_bin = ifelse(precip_treatment == "drought", 0,1), year_bin = ifelse(year == 2018, 0,1), burn_bin = ifelse(burn_treatment == "burn", 0,1), propagule_bin = ifelse(propagule_pressure == "no", 0,1)) %>%
  mutate(BRTE_density_sqrt = sqrt(BRTE_density)) %>%
  mutate(BRTE_density_sqrt_sqrt = sqrt(BRTE_density_sqrt)) %>%
  mutate(ELEL_density_sqrt = sqrt(ELEL_density)) %>%
  mutate(ELEL_density_sqrt_sqrt = sqrt(ELEL_density_sqrt)) %>%
  mutate(CETE_density_sqrt = sqrt(CETE_density)) %>%
  mutate(CETE_density_sqrt_sqrt = sqrt(CETE_density_sqrt)) %>%
  mutate(BRTE_canopy_cover_sqrt = sqrt(BRTE_canopy_cover)) %>%
  mutate(BRTE_canopy_cover_sqrt_sqrt = sqrt(BRTE_canopy_cover_sqrt)) %>%
  mutate(ELEL_canopy_cover_sqrt = sqrt(ELEL_canopy_cover)) %>%
  mutate(ELEL_canopy_cover_sqrt_sqrt = sqrt(ELEL_canopy_cover_sqrt)) %>%
  mutate(CETE_canopy_cover_sqrt = sqrt(CETE_canopy_cover)) %>%
  mutate(CETE_canopy_cover_sqrt_sqrt = sqrt(CETE_canopy_cover_sqrt)) %>%
  filter(precip_treatment != "control" & precip_treatment != "post_control")

shannon_diversity_canopy_cover_df_SEM_2018 <- shannon_diversity_canopy_cover_df_SEM %>% 
  filter(year == 2018)

shannon_diversity_canopy_cover_df_SEM_2019 <- shannon_diversity_canopy_cover_df_SEM %>% 
  filter(year == 2019)

shannon_diversity_canopy_cover_df_SEM_2020 <- shannon_diversity_canopy_cover_df_SEM %>% 
  filter(year == 2020)

```


#.
# 2018 lmer
# @models
```{r}
# PSEM 1
psem_A_2018 <- lmer(BRTE_density_sqrt ~ (1|block) + (1|whole_plot) + (1|split_plot) + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2018)

model_visualization(psem_A_2018)

psem_B_2018 <- lmer(shannon_diversity_canopy_cover ~ (1|block) + (1|whole_plot) + (1|split_plot) + BRTE_density_sqrt + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2018)

model_visualization(psem_B_2018)
```

```{r}
psem_vegetation_2018_A_no_prop <- psem(psem_A_2018, psem_B_2018)

```


```{r}
coefs(psem_vegetation_2018_A_no_prop)
```



```{r}
summary(psem_vegetation_2018_A_no_prop)
```

#.
# 2019 lmer
# @models
```{r}

psem_A_2019 <- lmer(BRTE_density_sqrt ~ (1|block) + (1|whole_plot) + (1|split_plot) + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2019)

model_visualization(psem_A_2019)

psem_B_2019 <- lmer(shannon_diversity_canopy_cover ~ (1|block) + (1|whole_plot) + (1|split_plot) + BRTE_density_sqrt + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2019)

model_visualization(psem_B_2019)
```

```{r}
psem_vegetation_2019_A_no_prop <- psem(psem_A_2019, psem_B_2019)

```


```{r}
coefs(psem_vegetation_2019_A_no_prop)
```


```{r}
summary(psem_vegetation_2019_A_no_prop)
```


#.
# 2020 lmer
# @models
```{r}

psem_A_2020 <- lmer(BRTE_density_sqrt ~ (1|block) + (1|whole_plot) + (1|split_plot) + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2020)

model_visualization(psem_A_2020)

psem_B_2020 <- lmer(shannon_diversity_canopy_cover ~ (1|block) + (1|whole_plot) + (1|split_plot) + BRTE_density_sqrt + burn_bin + rodent_bin + precip_bin, data = shannon_diversity_canopy_cover_df_SEM_2020)

model_visualization(psem_B_2020)
```

```{r}
psem_vegetation_2020_A_no_prop <- psem(psem_A_2020, psem_B_2020)

```



```{r}
coefs(psem_vegetation_2020_A_no_prop)
```


```{r}
summary(psem_vegetation_2020_A_no_prop)
```